---
title: "p8105_hw1_sw3879"
author: "Siqing Wang"
date: "2023-09-18"
output: github_document
---
## Problem 1

Importing the moderndive tidyverse library 

```{r loading libraries and data file}
library(moderndive)
data("early_january_weather")
library(tidyverse)
```
The early January weather dataset contains `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. 
This dataset contains the following variables: `r names(early_january_weather)`
By viewing this dataset, there are missing values in the wind_gust and pressure column that might impact later analyses. 

The mean temperature is `r mean(pull(early_january_weather, temp))` #round this 

```{r plotting}
library(ggplot2)
ggplot(early_january_weather, aes(x = hour, y = temp, color = humid)) + geom_point() + labs(title = "Early January Weather Temperature vs. Time")
ggsave(filename = "HW1_problem1_plot.pdf")
```

## Problem 2
Constructing the dataframe and taking the mean of each column 
```{r constructing dataframe and calculating mean}
p2_df = tibble(
  rs = rnorm(10, mean = 0, sd = 1),
  log = rs > 0,
  char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  fac = factor(c("high", "high", "high", "medium", "medium", "medium", "medium", "low", "low", "low"))
)
mean(pull(p2_df, rs))
mean(pull(p2_df, log))
mean(pull(p2_df, char))
mean(pull(p2_df, fac))
```
Mean can be calculated from the random sample and the logical vector, but not the character or factor vector. 

Converting the logical, character, and logical vector into numeric
```{r converting into numeric, eval=FALSE}
as.numeric(pull(p2_df, log))
as.numeric(pull(p2_df, char))
as.numeric(pull(p2_df, fac))
```

The logical and factor vectors can be coerced into numeric format, but not the character vector. 






